### 2020-03-08 README.Rmd
Vignettes and bug squashing.
Fixed a problem with README.

# Create a listdown object.
ld <- listdown(load_ld_expr = readRDS("pres-list.rds"), # The expression to load pres_list.
               package = "ggplot2",                     # The packges needed to render plots.
               decorator = list(ggplot = identity))     # What to do with the pres_list elements.

@@

# Create a listdown object.
ld <- listdown(load_ld_expr = readRDS("pres-list.rds"), # The expression to load pres_list.
               package = "ggplot2",                     # The packges needed to render plots.
               decorator = list(ggplot = identity))     # What to do with the plot types.

@@

>>>>

# Create a listdown object.
ld <- listdown(load_cc_expr = readRDS("pres-list.rds"), # The expression to load pres_list.
               package = "ggplot2",                     # The packges needed to render plots.
               decorator = list(ggplot = identity))     # What to do with the pres_list elements.

@@

# Create a listdown object.
ld <- listdown(load_cc_expr = readRDS("pres-list.rds"), # The expression to load pres_list.
               package = "ggplot2",                     # The packges needed to render plots.
               decorator = list(ggplot = identity))     # What to do with the plot types.

# Output an html document to a string.
doc <- c(
  ld_rmarkdown_header("Anscombe's Quartet",
                      author = "Francis Anscombe",
                      date = "1973"),
  ld_make_chunks(ld))

@@

```{r cleanup, echo = FALSE, warning = FALSE, error = FALSE}
unlink("pres-list.rds")
```
